---
title: "Consistency Report - Omni-benchmark"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=100, dplyr.print_max = 50)
```


## Hard-coded things, packages


```{r packages-sheets, message=FALSE, warning=FALSE}

# build self-contained HTML
#rmarkdown::render("analysis/02-omni-meta-combine-explore.Rmd", rmarkdown::html_document())

suppressPackageStartupMessages({
    #library(shiny)
    library(googlesheets4)
    library(dplyr)
    library(readr)
    library(DT)
    library(ggplot2)
    library(tidyr)
    library(ggrepel)
})

output_dir <- here::here("output")

options(gargle_oauth_email = TRUE)
stub <- "https://docs.google.com/spreadsheets/d/"
answers_sheet <- paste0(stub, 
                        "1ZMdGOv_ifRv9AWY-pIrXdzI4j9upeEvCI2aeRdLe94E") # restricted



```

The purpose of this document is to consolidate the reviews into a single response for each benchmark paper. The results are stored below in RDS files, and then used in the next document to make the figures for the paper. Here, some spot checks are added to check for consistency of answers.

## Answers


```{r papers, fig.width=14, fig.height=10, message=FALSE, warning=FALSE}

suppressMessages({
answers <- googlesheets4::read_sheet(answers_sheet) %>%
  tidyr::replace_na(list(`simulator(s)`="–"))
})

w <- grep("Degree to which code to re-run benchmark is extensible",
     colnames(answers))
colnames(answers)[w] <- "Degree to which code to re-run benchmark is extensible"

w <- grep("Whether performance results are explorable",
     colnames(answers))
colnames(answers)[w] <- "Whether performance results are explorable"

w <- grep("Whether any provenance (e.g., tracking of running of methods on datasets, logging, common workflow language) is used?",
          colnames(answers), fixed = TRUE)
colnames(answers)[w] <- "Whether any provenance is used"

answers_g <- answers %>% group_by(title) 
dim(answers_g)

answers_g %>% tally() %>% filter(n==1)

answers_g %>% tally() %>% pull("n") %>% table

keep <- answers_g %>% tally() %>% filter(n>=2) %>% pull(title)
answers_g <- answers_g %>% filter(title %in% keep)
dim(answers_g)


cn <- colnames(answers_g)
remove <- c("Details notes","Timestamp",
            "GitHub username of reviewer",
            "title","General info notes",
            "Repository links","Availability Notes",
            "Licence used for benchmark code",
            "Details notes")
cn <- setdiff(cn, remove)
names(cn) <- cn


numeric_cols <- c("Degree to which authors are neutral",
                  "Number of methods evaluated",
                  "Degree to which code is available",
                  "Number of datasets used in evaluations",
                  "Degree to which code to re-run benchmark is extensible",
                  "Number of criteria used for assessment")

categ_cols <- c("Type of workflow system used",
                "Whether input data used by the methods is available",
                "Whether synthetic data is available",
                "Whether results (methods run on data) are available",
                "Whether performance results (results compared to ground truth) are available",
                "Whether performance results are explorable",
                "Whether software versions (of all software) are tracked",
                "Whether methods are run / made available within containers",
                "Whether a preprint was posted before publication",
                "Type of benchmark",
                "Whether parameter space of methods was explored beyond defaults",
                "Whether any provenance is used")

union_cols <- c("Licence used for benchmark code",
                "For the methods benchmarked, what is/are the primary language/s they are written in?",
                "What secondary measures were assessed?")


setdiff(cn, c(numeric_cols, categ_cols, union_cols))


```

# Aggregate multiple responses

```{r plotters, fig.width=14, fig.height=10, message=FALSE, warning=FALSE}


answers_num_agg <- answers_g %>% select("title", all_of(numeric_cols)) %>% 
  summarise_all(median)

answers_cat_agg <- answers_g %>% select("title", all_of(categ_cols)) %>% 
  summarise_all(unique)

# clunky but does it ..
consolidate_unions <- function(u) {
  u <- unique(na.omit(u))
  if(length(u)==0)
    return("")
  if(length(u) == 1)
    return(u)
  else {
    u <- strsplit(u, ", ", fixed = TRUE)
    u <- unlist(u)
    return(paste0(unique(u), collapse = ", "))
  }
}

answers_union_list <- answers_g %>% select("title", all_of(union_cols)) %>% 
  split(answers_g$title)
answers_union_agg <- lapply(answers_union_list,
                            function(v) apply(v, 2, consolidate_unions)) %>%
  bind_rows
k <- answers_union_agg$`What secondary measures were assessed?`
answers_union_agg$`What secondary measures were assessed?`[k==""] <- "None"


answers_agg <- answers_num_agg %>% 
  left_join(answers_cat_agg, by = "title") %>%
  left_join(answers_union_agg, by = "title")
# which(answers_union_agg == "", arr.ind = TRUE)


table(answers_agg$`Type of workflow system used`)

table(code_available = round(answers_agg$`Degree to which code is available`),
      workflow_used = answers_agg$`Type of workflow system used`)


saveRDS(answers_agg, file=file.path(output_dir,"answers_agg.rds"))
saveRDS(numeric_cols, file=file.path(output_dir,"numeric_cols.rds"))
saveRDS(categ_cols, file=file.path(output_dir,"categ_cols.rds"))
saveRDS(union_cols, file=file.path(output_dir,"union_cols.rds"))

```


## Sessioninfo
```{r sessioninfo, message=FALSE, warning=FALSE}
sessionInfo()
#devtools::session_info()
```

